Public Gender Egalitarianism: A Dataset of Dynamic Comparative Public Opinion Toward Egalitarian Gender Roles in the Public Sphere

### 2020-12-27 paper/dcpo_gender_roles.Rmd
draft first paragraph

# Introduction

<!-- Gender egalitarian attitude has been grown over the decades not only in developed countries but also in developing societies [@boehnke2011gender]. -->
<!-- With the affluent variance in the gender egalitarian attitude around the world, scholars propose innovative research questions about the influence of gender egalitarian attitudes and its determinants. -->
<!-- For example, the association between gender egalitarian attitudes and women's political behavior [@krauss1974political], gender inequalities [@bianchi2012housework], women's descriptive representation in parliaments [@paxton2003women] have been examined. -->
<!-- However, the lack of cross-national time-series index prevents us from unveiling the cause and effect of gender egalitarian attitudes. -->
<!-- Very few cross-national time-series measures of gender egalitarianism exist and there is no consensus on the measures. -->
<!-- Even though a gender egalitarian index developed by @mcdaniel2008measuring exists, it only deals with limited number of countries (n=38) and with the fourth wave of World Value Survey (WVS) conducted between 1999 and 2004. -->

<!-- To overcome this limitation, we develop a comparable cross-national over time measure about gender egalitarian view in the public sector through the DCPO package for R [@Solt2020a].  -->
<!-- Our new index is based on data from 62 survey datasets from 1972 to 2020, which includes 224,640 observations.  -->
<!-- The newly developed gender egalitarian index provides opportunities for scholars to evaluate the generalizability of existing theories with large-N analysis, test the cause and effect of gender egalitarian attitudes, and build new theories with the preliminary statistical analysis. -->
<!-- The index provides an opportunity to descriptively examine how the attitudes have been changed over decades and why there are variations among countries with different political institutions, culture, religion, and other country specific factors. -->
<!-- We also can test the long-lasting question suggested by @krauss1974political about whether the differences in political behavior such as protests, voting, political volunteerism, and feminist movement of men and women are attributed to biological differences or public opinion on the gender role. -->
<!-- Moreover, the index makes it possible to unveil the relationship between gender egalitarianism and women's mobilization and representation [@erickson2002gender; @klein2013gender; @paxton1997women]. -->
<!-- Furthermore, by measuring cross-national time-variant attitudes toward gender egalitarianism, our index positions researchers to ask questions about how public opinion relates to the macrolevel processes of gender, such as the relationship between public opinion about gender roles and policy decisions [@stimson1995dynamic; @lax2009gay; @Wwlezien2017public], public opinion and political institutions [@bartels2009explaining; @grieco2011let; @nir2015institutions], and the public opinion and the makeup of national militaries [@brooks2011war; @eichenberg2016gender; @lizotte2017gender]. -->

<!-- This article proceeds with the following order.  -->
<!-- First, we discuss multi-dimensionality in egalitarian gender role and the reasons why we focus on the public sector. -->
<!-- Next, we illustrate the data source we used to build our index. -->
<!-- Then, the estimates of egalitarian gender role about 120 countries from 1972 to 2020 is introduced. -->
<!-- Lastly, we provide examples of how the new index about egalitarian gender role can be used and conclude.     -->
<!-- Gender egalitarianism does not have only one dimension but a multi-dimension. -->
<!-- Generating a measure of egalitarian gender roles without the classification may cause multidimensionality problem since people might have different opinions about gender roles by the dimensions. -->
<!-- For instance, some people have a more egalitarian veiw about the gender role in public sector rather than in private sector, while others do not. -->
<!-- To be specific, some might think that men and women should be treated and promoted equally at work, but that women should be in charge of housework. -->
<!-- Also, others may argue that both men and women can succeed as politicians, while saying that women are responsible for parenting. -->
<!-- The multi-dimensionality problem is relatively not salient if people in a society have an egalitarian view of all dimensions. -->
<!-- However, if we disregard this kind of multi-dimensionality given that there are some variations of gender egalitarain opinions by dimensions, we will not be able to measure gender egalitarianism properly in the various dimensions that people have. -->

# Focusing on Public Opinion Toward Gender Equality in the Public Sphere

@@

>>>>

Collective attitudes toward the appropriate roles of women and men in society---whether labeled culture or ideology or public opinion---constitute one of the primary explanations for women's exclusion from political power and policy influence [see, e.g., @Yates2017, 103-104; @Paxton2021, 113-114].
Yet even a half century after @RuleKrauss1974 [, 1719] called in the pages of the _APSR_ for more data to be collected on these collective attitudes, what we have available to us remains inadequate for fully examining their causes and consequences.
In the decades since, national and cross-national surveys have included a plethora of relevant questions, but sustained focus has been scant and the variety of these survey items renders the resulting data incomparable.
As a consequence, cross-national research has been constrained to study countries at just one or a few time points [see, e.g., @Paxton2003; @Alexander2012; @Ruedin2012; @Glas2020] or to rely on proxies such as predominant religion or the percentage of women in other offices [see, e.g., @Claveria2014; @Barnes2018].
Broadly cross-national and longitudinal investigation of, for example, the argument that such "attitudes influence both the supply of, and demand for, female candidates" has remained a topic for future research [@Paxton2010, 47].

@@

In this letter, we present the Public Gender Egalitarianism (PGE) database,
